Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2018-02-16 paper.tex
oka
yea

A multi-notch search is a remedy to the trade-offs caused by choosing a narrow (few ppm) or wide (few Da) precursor mass tolerance during a traditional narrow-window search.
It is not novel, and many useful search tools such as Tandem, MSGF+, Coment, MSFragger, Sequest have this search functionality under names such as "isotope error option".
This limited multi-notch search allows mass differences between precursor and theoretical peptides of 0, 1.0029 and 2.0054 Da, but it limits the width around these three mass differences to a few ppm (e.g. 1-20 ppm).
This approach provides a means of getting an increased number of correct identifications while mitigating problems with incorrect identifications.
This alternative would appear to result in loss of identification of co-isolated peptides, but MetaMorpheus is programmed to handle this problem by identifying multiple co-isolated precursor masses (see section below).

@@

The results of a multi-notch search are assessed using notch-specific FDRs, computed individually for each notch, similarly to MsFragger.

>>>>

A multi-notch search is a remedy to the trade-offs caused by choosing a narrow (few ppm) or wide (few Da) precursor mass tolerance during a traditional narrow-window search.
It is not novel, and many useful search tools such as Tandem, MSGF+, Comet, MSFragger, Sequest have this search functionality under names such as "isotope error option".
This limited multi-notch search allows mass differences between precursor and theoretical peptides of 0, 1.0029 and 2.0054 Da, but it limits the width around these three mass differences to a few ppm (e.g. 1-20 ppm).
This approach provides a means of getting an increased number of correct identifications while mitigating problems with incorrect identifications.
This alternative would appear to result in loss of identification of co-isolated peptides, but MetaMorpheus is programmed to handle this problem by identifying multiple co-isolated precursor masses (see section below).

@@

The results of a multi-notch search are assessed using notch-specific FDRs, computed individually for each notch, similarly to MSFragger.
It is important to note that there exist post-processing tools that would push identifications with unknown mass shifts and large numbers of missed cleavages down the list, such as the PeptideProphet extended mass model.
